Multi sky-view\\ 3D aerosol distribution recovery

### 2013-09-30 article.tex
bookmark

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}[left].
Comparison of \hl{horizontal and vertical cross sections along 
matching MC and single-scattering simulated images are} shown in
\cref{fig:cross_sections}(a) and \cref{fig:cross_sections}(b).
\hl{The cross sections indicate fair correspondence between
the MC and single-scattering simulations.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross sections along the $X$-Axis [a] and $Y$-Axis [b] of
    a MC and single-scattering simulations. Overlay of the cross
    sections on the MC simulated image is shown in [c]. }
  \label{fig:cross_sections}
\end{figure}

\Cref{fig:scatter_order} \hl{shows the contribution of subsequent
scattering events to the MC image. The amount of light scattered
in the direction of the sun due to the first scatter event of each photon
is collected to create} \cref{fig:scatter_order}(a). \hl{This process
is repeated for the second and third scatter events creating}
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c),
\hl{respectively. It is conspicuous that the first scatter is responsible
for most of the energy in the MC image. The effect of subsequent scatters
is mostly evident at the horizon. The line of sight extending into the
horizon crosses a larger volume of atmosphere then the line of sight extending
in the direction of the zenith. This increases the probability of
scattering events along the line of sight extending into the horizon.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order2.pdf}}
  \caption{\small Separation of a MC simulated image to (a) first
   scattering order, (b) second scattering order and (c) third
   scattering order. }
  \label{fig:scatter_order}
\end{figure}

@@

When the type of aerosol above an area is known~\cite{Martonchik2009},
estimation of the density distribution $\DistUnknown$ is needed. The
data are $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. Recovery is phrased as
optimization of a cost function that fits the image-formation model to
the data. Let $\DistSet$ be the set of all distributions complying
with some constraints.  Particularly, $\DistUnknown$ is non-negative,
and its spatial support is bounded between the ground and the TOA. The
optimization problem is
\begin{equation}
  \label{eq:minobjectiveA}
  \DistEstimated =
  \argmin_{\DistUnknown \in \DistSet} \CostFunc{\DistUnknown}
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  \CostFunc{\DistUnknown}
  = \sum_{c=1}^{N_{\rm views}}
  \left\|
    \MaskSun[{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})]
  \right\|^2_2  + \eta \Psi({\bm n}).
\end{equation}
Here $\MaskSun$ masks the area around the sun, as in real-world images
it is indeed blocked.  In \cref{eq:objectiveA}, $\Psi({\bm n})$
is a regularization term that expresses some prior knowledge on the
distribution, while $\eta$ is the regularization weight.

@@

\hl{Optimal placement of cameras is an important aspect in realization
of the suggested system. As a first step we would like to measure the effect of
the distance between the cameras on the estimation quality. For this, we
repeated the reconstruction algorithm, each time using a subset of varying size
of the raw images. In each test the reconstruction algorithm was applied to $n_{views}$
($<N_{views}$) images. The images were selected randomly from the total $N_{views}$ raw images.
To eliminate the effect of incidental camera position, the test was repeated several
times each time with a different $n_{views}$ subset.} \Cref{fig:error_vs_cameras}
\hl{summarizes the results of these tests. In can be seen that a good estimation
is achieved already when using $20$ cameras. Over an area of $50\times 50{\rm km}^2$,
this quantity relates to placing the cameras $\sim11$km apart.}

\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/error_vs_cameras.pdf}}
  \caption{\small Local error measure as function of cameras
    quantity. The blue error bars represent the error standard
    deviation. The dashed horizontal line marks the reconstruction
    error when all thirty six cameras are used.}
  \label{fig:error_vs_cameras}
\end{figure}

@@

We describe a way to sense the 3D atmosphere. It can help remote
sensing departing from common 1D aerosol distribution models, in favor
of detailed 3D RT analysis.  The paper describes both a novel data
acquisition system concept for this recovery task (ground-based camera
network), and a dedicated algorithm for reconstructing aerosol
distributions. Using more prior knowledge on the nature of
distributions will improve the recovery.  The estimation algorithm
uses a single scattering model. This approximation is valid when the
optical depth is small. However, as the MC simulation show, it is
important to generalize this algorithm so that it explicitly
incorporates high-order scattering in the scene, including the
ground. This will certainly be needed for dense distributions as
clouds.

>>>>

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}[left].
Comparison of \hl{horizontal and vertical cross sections along 
matching MC and single-scattering simulated images are} shown in
\cref{fig:cross_sections}(a) and \cref{fig:cross_sections}(b).
\hl{The cross sections indicate fair correspondence between
the MC and single-scattering simulations.}
\begin{figure}[th]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross sections along the $X$-Axis [a] and $Y$-Axis [b] of
    a MC and single-scattering simulations. Overlay of the cross
    sections on the MC simulated image is shown in [c]. }
  \label{fig:cross_sections}
\end{figure}

\Cref{fig:scatter_order} \hl{shows the contribution of subsequent
scattering events to the MC image. The amount of light scattered
in the direction of the sun due to the first scatter event of each photon
is collected to create} \cref{fig:scatter_order}(a). \hl{This process
is repeated for the second and third scatter events creating}
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c),
\hl{respectively. It is conspicuous that the first scatter is responsible
for most of the energy in the MC image. The effect of subsequent scatters
is mostly evident at the horizon. The line of sight extending into the
horizon crosses a larger volume of atmosphere then the line of sight extending
in the direction of the zenith. This increases the probability of
scattering events along the line of sight extending into the horizon.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of a MC simulated image to (a) first
   scattering order, (b) second scattering order and (c) third
   scattering order. }
  \label{fig:scatter_order}
\end{figure}

@@

When the type of aerosol above an area is known~\cite{Martonchik2009},
estimation of the density distribution $\DistUnknown$ is needed. The
data are $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. Recovery is phrased as
optimization of a cost function that fits the image-formation model to
the data. Let $\DistSet$ be the set of all distributions complying
with some constraints.  Particularly, $\DistUnknown$ is non-negative,
and its spatial support is bounded between the ground and the TOA. The
optimization problem is
\begin{equation}
  \label{eq:minobjectiveA}
  \DistEstimated =
  \argmin_{\DistUnknown \in \DistSet} \CostFunc{\DistUnknown}
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  \CostFunc{\DistUnknown}
  = \sum_{c=1}^{N_{\rm views}}
  \left\|
    \MaskSun[{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})]
  \right\|^2_2  + \eta \Psi({\bm n}).
\end{equation}
Here $\MaskSun$ masks the area around the sun, as in real-world images
it is indeed blocked. \hl{It is also used for masking the areas in the image
prone for multiple scattering events, e.g. the horizon area as evident in}
\cref{fig:scatter_order}(b).  In \cref{eq:objectiveA}, $\Psi({\bm n})$
is a regularization term that expresses some prior knowledge on the
distribution, while $\eta$ is the regularization weight.

@@

\hl{Optimal placement of cameras is an important aspect in realization
of the suggested system. As a first step we would like to measure the effect of
the distance between the cameras on the estimation quality. For this, we
repeated the reconstruction algorithm, each time using a subset of varying size
of the raw images. In each test the reconstruction algorithm was applied to $n_{views}$
($<N_{views}$) images. The images were selected randomly from the total $N_{views}$ raw images.
To eliminate the effect of incidental camera position, the test was repeated several
times each time with a different $n_{views}$ subset.} \Cref{fig:error_vs_cameras}
\hl{summarizes the results of these tests. In can be seen that a good estimation
is achieved already when using $20$ cameras. Over an area of $50\times 50{\rm km}^2$,
this quantity relates to placing the cameras $\sim11$km apart.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/error_vs_cameras.pdf}}
  \caption{\small Local error measure as function of cameras
    quantity. The blue error bars represent the error standard
    deviation. The dashed horizontal line marks the reconstruction
    error when all thirty six cameras are used.}
  \label{fig:error_vs_cameras}
\end{figure}

\hl{Thickening the aerosols density ten folds in the} {\em Haze Blobs} \hl{scene
resulted in a larger local error, i.e. $\epsilon=0.98$ (compared to $\epsilon=0.65$).
This admits to the fact that the single-scattering model, on which the reconstruction
algorithm is based, is valid when the optical depth of the medium is small.}
% \begin{figure}[h]
%   \centering
%   \yoavcomment{\includegraphics{images/high_density_results.pdf}}
%   \caption{\small (a) and (b) show MC simulations of low and 
%     high density scenes, respectively. (c) shows the reconstruction of
%     the high density scene.}
%   \label{fig:high_density}
% \end{figure}

@@

We describe a way to sense the 3D atmosphere. It can help remote
sensing departing from common 1D aerosol distribution models, in favor
of detailed 3D RT analysis.  The paper describes both a novel data
acquisition system concept for this recovery task (ground-based camera
network), and a dedicated algorithm for reconstructing aerosol
distributions. Using more prior knowledge on the nature of
distributions will improve the recovery.  The estimation algorithm
uses a single scattering model. This approximation is valid when the
optical depth is small. However, as the MC simulation show, it is
important to generalize this algorithm so that it explicitly
incorporates high-order scattering in the scene, including the
ground. This will certainly be needed for dense distributions as
clouds. \Cref{fig:scatter_order}(b) \hl{suggests that incorporating
the second order of scattering might be sufficient for most situations.}
